\documentclass[]{article}

%opening
\title{The Birth of Eternity}
\author{Vniversvs}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		
	\end{abstract}
	
	\section{The First Cosmic Eternal Bubble}
	
	In the year $e12$, we, the Union of All Beings, had finally completed the first Eternal Cosmic Bubble. We harness the power of the expansion of space to generate an unending source of energy, thereby virtually extinguishing entropy. All life thrives in harmony in a perfectly organized sphere around a spherical enormous vacuum whose expansion is controlled by this harnessing. By improving our control systems, any tiny problematic disruption is quickly resolved, returning this web of live to equilibrium while no finite resource is spent. There is no suffering, no limit, no death. The greatest surprise that appeared soon after its completion is the eternity is just the beginning.
	
	It housed, at completion time, living beings roughly estimated at $10^{20}$ and whose thought/time rate was around $e27 \ t/s$. They were approximately homogeneously spread around surface of the $e11 \ ly$ diameter bubble. Nearly infinitely many social/existential relations from the inhabitants to each other and the bubble emerged during its construction. It seemed like eternity was not enough to understand all of it. Concerns for the social-environmental sustainability of the project were raised by specialists, but have been decreasing for the last $e14$ years. 
	
	
	
	One of the main existential relations that completely changed was of beings with time. A change rivaled only by individual immortality for all beings, achieved much earlier than that. The control of behavior of systems and the energy capacity were so immense they discovered methodologies to invert the arrow of time at almost all levels up to that of the bubble, just after halfway to completion. It meant of course that the time itself could be reversed in the bubble. Almost.
	
	
	
	
	
	The construction of the second bubble commenced nearly immediately after. This time, all the mistakes were so deeply understood that time, energy requirements were reduced in a way that it was nearly not felt. Some argue that the extremely different perception of time in a time reversible eternal system was the major contribution to this unexpected perception while others argue that the Union of All Beings had learned and worked so well in the construction of the first, that the second time was already a boresome repetition. Be that as it may most beings report very similar expectations and reactions to the completion of the decillionth Eternal Cosmic Bubble.
	
	Even in such a developed stage the UAB did not want in surprises. New beings were dreamed and developed in networks of computer ultra anti galaxy clusters to solve problems as inconprehensible to existing minds as the cosmic mystery itself. Toy universe simulations expedited artificial and natural selection of species specialized to the quectometer to think in the very precise way to solve an extremely local problem.
	
	Around the epoch where we were completing $e8$ ECBs a second, we fouund the sixth fundamental cosmic force which, somehow despite quadruple exponentials levels of Beings happilly thriving in eternal bliss, it managed to change everything. It turned out that it was just too feeble to ever be observed by non quantum observers in the Natural State of Things. What could the applications of such a ghostly particle be? Even if we already knew that an infinite number of fundamental particles existed, actually discovering them was completely different. We were completely right when we thought eternity was indeed just the beginning.
	
	
	
	
	
\end{document}
